The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-02 manuscript.Rmd
better title (maybe)

---
#author: Fran\c{c}ois Michonneau
title: "Data-driven approaches to identifying knowledge gaps in marine invertebrate biodiversity"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    #includes:
    #  before_body: ../template/doc_prefix.tex
    #  in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
fontsize: 12pt
link-citations: yes
csl: nature.csl
bibliography: /home/francois/Library/dark-plankton.bib
---

>>>>

---
#author: Fran\c{c}ois Michonneau
title: "The state of knowledge for marine invertebrate biodiversity in the continental US"
date: ' ' #'`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    #includes:
    #  before_body: ../template/doc_prefix.tex
    #  in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
fontsize: 12pt
link-citations: yes
csl: nature.csl
bibliography: /home/francois/Library/dark-plankton.bib
---
